Blum axioms and nondeterministic computation of functions

### 2016-04-19 paper.tex
paper.tex: Rewrite section about Valiant's definition.

As observed by Krentel,
the definition of $\OptP$ was achieved by applying
an associative and commutative operator to the set of values
that the nondeterministic machine returns.
Thus,
for every different operator we choose,
we have an alternative definition of nondeterministic computation of functions.
We mention only one such alternative definition,
due to Valiant \cite{Valiant1979}.

\begin{definition}
    If every branch of the computation of $M$ on $x$ halts,
    define the value returned by $M$ on $x$
    as being the number of different accepting branches of computation.
\end{definition}

In the same way that Krentel defined his $\OptP$ class using polynomial bounds,
Valiant's $\#\P$ class is the set of all functions
that can be computed in polynomial time by nondeterministic machines
according to the above definition.

>>>>

Valiant takes a different approach to defining how to extract a value
from the set of strings written by all branches of a computation:
just count the number of accepting branches.

\begin{definition}[Valiant's definition]
    A nondeterministic machine $M$ computes a function $f: \{0, 1\}^* \to \mathbb N$ if,
    for every input $x$,
    $M$ halts on every branch\footnote{
        Valiant did not include the requirement of halting in his definition,
        but we will include it to avoid having the same problems
        of Hopcroft and Ullman's definition.
    }
    and the number of accepting branches of computation is $f(x)$
    \cite[p.~191]{Valiant1979}.
\end{definition}
This approach also yields acceptable Gödel numberings and Blum complexity measures.

The class $\#\P$ is the set of functions computed in polynomial time,
under Valiant's definition.
$\#\P$-completeness is defined through oracles;
that is, a function $f$ is $\#\P$-complete if $f \in \#\P$
and $\#\P \subseteq \FP^f$
(that is, every function of $\#\P$ can be computed by a deterministic machine
with access to an oracle that computes $f$)
\cite[p.~191]{Valiant1979}.

Since there are reductions of the Boolean satisfiability problem
that preserves the number of accepting paths\footnote{
    Such reductions are called \emph{parsimonious} \cite[p~346]{AroraBarak2009}.
},
the problem of counting the number of satisfying assignments is $\#\P$-complete.
Valiant also proves less trivial problems are $\#\P$-complete,
like the task of computing the permanent of a matrix,
even when the matrix is restricted to have only $0$ and $1$ as entries
\cite[p.~194]{Valiant1979}.
Therefore,
this definition is also flexible, like Krentel's.
